The State of Graph Processing

### 2016-12-14 taxonomy/taxonomy.tex
Added a template for graph processing taxonomy.
This will eventually describe the current state of the art.

\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{hyperref}
\usepackage{pgfplotstable, booktabs}
\pgfplotsset{compat=1.12}
\usepackage{datetime}

@@

\begin{document}
\title{Parallel Graph Processing Report\vspace{-2em}}
\author{}
\date{Generated \today\ at \currenttime}
\maketitle

This report was automatically generated from \verb|PATH_TO_MAKEFILE| on \verb|HOSTNAME|.

\section{Machine Specifications}
These data were gathered from \verb|specs.csv|. If these results are not complete enough, try running \verb|get-hwinfo.sh| again and run the command it suggests as root.

% TODO: Make this a pgfplotstable with an automatically generated csv.
\begin{table}[htb]
	\centering
% Keep in mind you can do this at the beginning: string replace={s1}{s2}
	\pgfplotstabletypeset[
	header=false,
	col sep=tab,
	string type,
    every head row/.style={output empty row, before row=\bottomrule},
	columns/0/.style={column type={|r|}},
	columns/1/.style={column type={l|}},
	every last row/.style={after row=\toprule},
	]{specs.csv}
	\caption{Machine specifications.}
	\label{tab:specs}
\end{table}

\section{Performance Results}
Performance in millions of traversed edges per second (MTEPS)

% TODO: Actually get this to autogenerate.
\begin{table}[htb]
	\centering
	\begin{tabular}{l|r|r|}
	 & PowerGraph & OpenG \\ \hline
	BFS & $87.4$ & $341$ \\ \hline
	SSSP & $1.09$ & $3.08$ \\ \hline
	\end{tabular}
	\caption{Performance Results}
	\label{tab:perf}
\end{table}

>>>>

\documentclass[11pt]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{hyperref}
\usepackage{pgfplotstable, booktabs}
\pgfplotsset{compat=1.12}
\usepackage{datetime}

@@

\begin{document}
\title{The State of Graph Processing}
\subtitle{APIs, Libraries, Platforms, and Programming Languages}
\author{Samuel Pollard}
\date{\today}
\maketitle

\section{Introduction}
